---
title: "HS uncertainty evalution"
author: "acs"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup}
library(dplyr)
library(tidyr)
library(ggplot2)

read_dir <- 'Uncertainty'
fig_dir <- 'figures/'


year_cutoff <- 2040
rms_cutoff <- 0.1


# Figure sizing info
title_size <- 14
axis_size <- 12
```

# read, reshape uncertainty time series

```{r, echo = FALSE}
pr_list <- list.files(read_dir, pattern = 'pr_',full.names = T)
tas_list <- list.files(read_dir, pattern = 'tas_', full.names = T)

# list of PR coeff metric files
pr_coef <- pr_list[grepl('coefficient', pr_list)]

# list of PR full files
pr_full <- pr_list[grepl('full', pr_list)]

# list of tas coef metric files
tas_coef <- tas_list[grepl('coefficient', tas_list)]

# list of tas full files
tas_full <- tas_list[grepl('full', tas_list)]


# for each list of files, read in, add variable-region-metric id info, append
uncertainties <- data.frame()
for(filename in pr_coef){
   # print(filename)
    f <- read.csv(filename, stringsAsFactors = F)

    f %>%
        mutate(var = 'pr',
               metric = 'coef',
               tmp = filename) %>%
        separate(tmp, into = c('trash', 'rgn', 'trash2'), sep = '_', extra = 'merge' ) %>%
        select(-trash, -trash2) %>%
        bind_rows(uncertainties,.) ->
        uncertainties
    rm(f)
}


for(filename in pr_full){
    #print(filename)
    f <- read.csv(filename, stringsAsFactors = F)

    f %>%
        mutate(var = 'pr',
               metric = 'full',
               tmp = filename) %>%
        separate(tmp, into = c('trash', 'rgn', 'trash2'), sep = '_', extra = 'merge' ) %>%
        select(-trash, -trash2) %>%
        bind_rows(uncertainties,.) ->
        uncertainties
    rm(f)
}

for(filename in tas_coef){
    #print(filename)
    f <- read.csv(filename, stringsAsFactors = F)

    f %>%
        mutate(var = 'tas',
               metric = 'coef',
               tmp = filename) %>%
        separate(tmp, into = c('trash', 'rgn', 'trash2'), sep = '_', extra = 'merge' ) %>%
        select(-trash, -trash2) %>%
        bind_rows(uncertainties,.) ->
        uncertainties
    rm(f)
}

for(filename in tas_full){
    #print(filename)
    f <- read.csv(filename, stringsAsFactors = F)
    
    f %>%
        mutate(var = 'tas',
               metric = 'full',
               tmp = filename) %>%
        separate(tmp, into = c('trash', 'rgn', 'trash2'), sep = '_', extra = 'merge' ) %>%
        select(-trash, -trash2) %>%
        bind_rows(uncertainties,.) ->
        uncertainties
    rm(f)
}

```


```{r}

# continue reshaping
uncertainties %>% 
    gather(uncertainty, value, -var, -metric, -rgn, - year) %>%
    distinct->
    uncert_long


uncert_long %>%
    filter(metric == 'full') %>%
    rename(full = value) %>%
    select(-metric) ->
    uncert_full


uncert_long %>%
    filter(metric == 'coef') %>%
    left_join(uncert_full, by = c('year', 'var', 'rgn', 'uncertainty')) ->
    coef_metric

```


#  Compare subsets to full

```{r}


coef_metric %>%
    filter(year >= year_cutoff) %>%
    group_by(rgn, var, metric, uncertainty) %>%
    summarize(rms = sqrt(mean((value-full)^2))) %>%
    ungroup ->
    coef_dist


coef_metric %>%
    filter(year >= year_cutoff) %>%
    group_by(rgn,  metric, uncertainty) %>%
    summarize(rms = sqrt(mean((value-full)^2))) %>%
    ungroup ->
    coef_dist2


```

## identify cutoff, patterns for each metric


```{r, message=FALSE}


ggplot(coef_dist, aes(x = rms, color = interaction(var, uncertainty))) + 
    geom_histogram()+
    facet_wrap(~var) +
    ggtitle('coef')

```

-spread is tighter for coef (most mass <0.17ish) but proj has fewer outliers for
P (more for T)

- so is 0.2 a fair cutoff for 'good' -> check HS figs

- if so, then do count > 0.2 for P,T for two coeff

## coef below cutoff

```{r}
coef_dist %>%
    filter(rms >=0.2) %>%
    select(rgn, var) %>%
    distinct %>%
    mutate(id = paste(rgn, var, sep='~')) ->
    coef_bad


coef_dist %>%
    filter(rms <0.2 & rms >= rms_cutoff) %>%
    select(rgn, var) %>%
    distinct  %>%
    mutate(id = paste(rgn, var, sep='~')) ->
    coef_questionable


knitr::kable(coef_questionable)
knitr::kable(coef_bad)


uncert_long %>%
    mutate(id = paste(rgn, var, sep='~')) %>%
    filter(year >= year_cutoff,
           metric == 'full' | metric == 'coef',
           id %in% coef_bad$id |
               id %in% coef_questionable$id) ->
    coef_rgn_plots


# ggplot()+
#     geom_line(coef_rgn_plots %>% filter(metric == 'full'),
#               mapping=aes(x = year, y = value, color = uncertainty), linetype = 1) +
#     geom_line(coef_rgn_plots %>% filter(metric == 'coef'),
#               mapping=aes(x = year, y = value, color = uncertainty), linetype = 2) +
#     facet_wrap(~id, nrow = 3) +
#     ggtitle('coef')




# Order stacks for HS fig
coef_rgn_plots %>%
    mutate(uncertainty = if_else(uncertainty == 'Inter.Annual.Variability', 'A.Inter.Annual.Variability',
                                 if_else(uncertainty == 'Scenario.Uncertainty', 'B.Scenario.Uncertainty',
                                         if_else(uncertainty == 'Model.Uncertainty', 'C.Model.Uncertainty',
                                                 'NA' )))) ->
    coef_rgn_plots

# ggplot()+
#     geom_bar(coef_rgn_plots %>% filter(metric == 'full'),
#              position = 'stack', stat = 'identity',
#               mapping=aes(x = year, y = value, color = uncertainty, fill = uncertainty)) +
#     scale_color_manual(values = c('darkorange', 'forestgreen', 'blue4')) +
#     scale_fill_manual(values = c('darkorange', 'forestgreen', 'blue4')) +
#     geom_bar(coef_rgn_plots %>% filter(metric == 'coef'),
#              position = 'stack', stat = 'identity',
#               mapping=aes(x = year, y = value, group = uncertainty), fill = NA, color = 'white', size= 0.1) +
#     #scale_color_manual(values = c('orange', 'green', 'blue')) +
#     facet_wrap(~id, nrow = 3) +
#     ggtitle('coef')




# Extract lines for coef:
coef_rgn_plots %>%
    filter(uncertainty != 'A.Inter.Annual.Variability',
           metric=='coef') %>%
    group_by(year, var, metric, rgn, id) %>%
    summarize(value = sum(value)) %>%
    ungroup() %>%
    mutate(uncertainty = 'B.Scenario.Uncertainty') %>%
    bind_rows(coef_rgn_plots %>%
                  filter(uncertainty == 'C.Model.Uncertainty',
                         metric=='coef'))  ->
    coef_rgn_plots2
```

```{r , fig.width=14, fig.height=10}
p_tas <- ggplot()+
    geom_bar(coef_rgn_plots %>% filter(metric == 'full', var =='tas'),
             position = 'stack', stat = 'identity',
              mapping=aes(x = year, y = value, color = uncertainty, fill = uncertainty)) +
    scale_color_manual(values = c('darkorange', 'forestgreen', 'blue4')) +
    scale_fill_manual(values = c('darkorange', 'forestgreen', 'blue4')) +
    geom_line(coef_rgn_plots2 %>% filter(var == 'tas'),
              mapping=aes(x = year, y = value, linetype = uncertainty), color = 'white') +
    facet_wrap(~rgn, ncol=6) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    ggtitle('Temperature') +theme_bw() +
     theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
           axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
           axis.title = element_text(size = axis_size), 
          plot.title = element_text(size = title_size),
          strip.text = element_text(size = axis_size),
          legend.key = element_rect(fill = 'grey')) + 
    ylab('fraction of total variance')

ggsave(paste0(fig_dir, 'temperature_HS_regions.png'), p_tas, width = 8, height =6, units = 'in')

p_tas

```

```{r , fig.width=14, fig.height=10}
p_pr <- ggplot()+
    geom_bar(coef_rgn_plots %>% filter(metric == 'full', var =='pr'),
             position = 'stack', stat = 'identity',
              mapping=aes(x = year, y = value, color = uncertainty, fill = uncertainty)) +
    scale_color_manual(values = c('darkorange', 'forestgreen', 'blue4')) +
    scale_fill_manual(values = c('darkorange', 'forestgreen', 'blue4')) +
    geom_line(coef_rgn_plots2 %>% filter(var == 'pr'),
              mapping=aes(x = year, y = value, linetype = uncertainty), color = 'white') +
    facet_wrap(~rgn, ncol=6) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    ggtitle('Precipitation') +theme_bw() +
     theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
           axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
           axis.title = element_text(size = axis_size), 
          plot.title = element_text(size = title_size),
          strip.text = element_text(size = axis_size),
          legend.key = element_rect(fill = 'grey')) + 
    ylab('fraction of total variance')

ggsave(paste0(fig_dir, 'precipitatoin_HS_regions.png'), p_pr, width = 8, height =6, units = 'in')

p_pr

```


# Spatial info for plots where 'good'


```{r, echo=FALSE}

library(sf)

shp <- st_read(dsn = 'IPCC-WGI-reference-regions-v4_shapefile/IPCC-WGI-reference-regions-v4.shp', stringsAsFactors = F)

# add a numerical region id
shp %>% 
  mutate(region_id = as.integer(row.names(.))) ->
  shp

# add coordinate info probably
shp1 <-  st_transform(shp, "+proj=longlat +ellps=WGS84 +datum=WGS84")

# extract
coords <- as.data.frame(st_coordinates(shp1))


# get a mean lon and lat value in each shape
coords %>%
  rename(lon = X, lat = Y, region_id = L3) %>%
  left_join(as.data.frame(shp) %>% select(region_id, Acronym), by = 'region_id') %>%
  filter(grepl('PO', Acronym)) %>% 
  # have to have lon on 0:360 so th pacific ocean behaves even though not
  # looking at that here
  mutate(lon_360 = if_else(lon >=0, lon, lon+360))%>%
  group_by(region_id) %>%
  summarise(mean_lon = mean(lon_360),
            mean_lat = mean(lat)) %>%
  ungroup  %>%
  mutate(mean_lon = if_else(mean_lon >= 0 & mean_lon <= 180, 
                            mean_lon, mean_lon - 360) ) ->
  mean_pts_PO

coords %>%
  rename(lon = X, lat = Y, region_id = L3) %>%
  left_join(as.data.frame(shp) %>% select(region_id, Acronym), by = 'region_id') %>%
  filter(!grepl('PO', Acronym)) %>% 
  # have to have lon on 0:360 so th pacific ocean behaves even though not
  # looking at that here
  group_by(region_id) %>%
  summarise(mean_lon = mean(lon),
            mean_lat = mean(lat)) %>%
  ungroup  %>% 
  bind_rows(mean_pts_PO)->
  mean_pts 


```


```{r, fig.width=14, fig.height=10, echo=FALSE}
# Join to the shape file and make sure this very simple way of
# doing things ends up with a lon lat that is actually in each region
shp %>%
    left_join(mean_pts, by = 'region_id') %>%
    left_join(coef_dist %>%
                  select(rgn, var) %>%
                  distinct, 
                  by = c('Acronym' = 'rgn'))->
  shp2

shp2 %>%
    mutate(id = paste(Acronym, var, sep = '~'),
           fill_color = if_else(id %in% coef_bad$id | id %in% coef_questionable$id,
                                0, 1),
           fill_color = if_else(fill_color == 1 & var == 'pr', 0.5, fill_color)) %>%
    group_by(Continent, Type, Name, Acronym, region_id, mean_lon, 
             mean_lat, geometry) %>%
    summarize(fill_color = sum(fill_color)) %>%
    ungroup %>%
    mutate(fill_color = if_else(fill_color == 0, 'Both Vars Flagged',
                                if_else(fill_color == 0.5, 'Precip only',
                                        if_else(fill_color ==1, 'Temp only',
                                                if_else(fill_color == 1.5, 'Precip and Temp', 'NA'))))) ->
    shp3



p_map <- ggplot() +
  geom_sf(data = shp3, mapping = aes(fill = fill_color)  ) +
  #geom_point(data = shp, mapping = aes(x = mean_lon, y = mean_lat), color = 'red') +
  geom_text(data = shp3, mapping = aes(label = Acronym, x = mean_lon, y= mean_lat), size = 4) +
  #ggtitle('coef') + 
    xlab('') + ylab('')+  labs(fill='')+
    theme(plot.margin=grid::unit(c(0,0,0,0), "mm")) 


p_map

ggsave(paste0(fig_dir, 'HS_success_map.png'), p_map, width = 14, height = 6, units = 'in')

```


# Notes

INteresting thing - because our region indices are focused around mid and end of
century, our HS figures tend to be closest there.

If we look over 2015 on for comparing metrics instead of 2040, we do see that the
latter half of the century is often better than first half even in the 'bad' HS



Differences over regions also interesting - if really care about Russian Arctic 
or Australia, proj is better. If care about Americas, Africa, Europe, Asia: Coef 
better.

-> given this is where most agriculture and people are, go with coefficient.

